Fusing Filters with Integer Linear Programming

### 2014-05-07 2014betterfusionforfilters/section/04-ILP.tex
ilp

If there is no edge between $i$ and $j$, the constraint simplifies to $-N \le \pi_j - \pi_i \le N$, which effectively means there is no constraint on the $\pi$ values. Note, however, that other edges may still constrain $i$ or $j$ by transitivity. \ben{If there is ``no constraint'' on the $\pi$ values then why bother adding the constraint at all?}

>>>>

If there is no edge between $i$ and $j$ and the two are not fused together, then $x_{ij} = 1$ and the constraint simplifies to $-N \le \pi_j - \pi_i \le N$, which effectively puts no constraint on the $\pi$ values.
Note, however, that other edges may still constrain $i$ or $j$.
